---
title: "Regular Expressions"
output: html_document
---

### Loading the Libraries
```{r}
library(ggplot2)
library(dplyr)
library(readr)
library(tidyverse)
library(reshape)
```

### Loading the Data and Converting to Tibble
```{r}
my_data <- read_csv("https://data.cityofnewyork.us/resource/h9gi-nx95.csv")
auto_accidents = as_tibble(my_data)
auto_accidents
```

## Fixing On Street Address

### Next, I converted the on_street_name into titlecase.
```{r}
auto_accidents$on_street_name = str_to_title(auto_accidents$on_street_name)
auto_accidents
```

### Next, I separated the on_street_name into the house number and street.
```{r}
auto_accidents = auto_accidents %>% extract(on_street_name, c('house_number', 'street'), '(\\S+)\\s+(.*)', convert = TRUE) 
auto_accidents
```

### Next, I created house_number_start which is the start of the house_number up to the last character.
```{r}
auto_accidents$house_number_start =  str_sub(auto_accidents$house_number,0,-2)
auto_accidents
```

### Then, if the last character of the house_number ended with a number from 0-9, I replaced it with its ordinal value. 
```{r}
auto_accidents$house_number_end = str_replace_all(str_sub(auto_accidents$house_number,-1), c("0"="0th","1" = "1st", "2" = "2nd", 
                                               "3" = "3rd", 
                                               "4" = "4th", "5" = "5th", "6"="6th", 
                                               "7" = "7th", "8" = "8th", "9" = "9th"))
auto_accidents
```

### Next, I joined the house_number_start and house_number_end back together with no spaces in betweem as house_number
```{r}
auto_accidents = auto_accidents %>% 
   unite(house_number, house_number_start, house_number_end, sep = "", remove = TRUE)
auto_accidents
```


### Then, I rejoined house_number and street back together as on_street_name with one space between them
```{r}
auto_accidents = auto_accidents %>% 
   unite(on_street_name, house_number, street, sep = " ", remove = TRUE)
auto_accidents
```

### Problems:

1. The method above doesn't always assign the write ordinal form. For example, 12 Avenue becomes 12nd Avenue. 

2. When the number is not in the first word of the string the method above also doesn't work.
For example, East 174 Street stays the same. 

3. Lastly, there is an issue with missing values becoming "NA" or "NANA" or "NANANA" with the string joins. 

## Vehicle Codes

### Lastly, I found that there are 34 distinct vehicle type code #1 values. 
```{r}
n_distinct(auto_accidents$vehicle_type_code1)
```

### Below are their codes.  
```{r}
unique(auto_accidents$vehicle_type_code1)
```
In my opinion these codes are confusing - there are two many different categories. 
One way to categorize them is by their passenger capacity and size (small, medium, large, extra-large). 

So, two passenger -small would be a Motorcycle and two passengers medium would be a coupe, two passengers large would be a pickup truck, and two passengers extra-large would be a six+ wheeler truck. 

Regex might be too complicated for this. It would be easiest to replace the values with str_replace_all and a list of the replacements, as above. 
